### 2022-07-22 main/chapter_2ljets.tex
clarify extended fits Poisson stuff

Worse, I disregarded the idea that every region should have a large
background expectation.
Normally, this is justified by the limitations of approximate statistical
methods, which work
``from as few as $\mathcal{O}(10)$ data events''~\cite{histfitter2014}.
But the Poisson likelihood works for infinitesimally small
expectations~\cite{skilling2009cosmology}, and in the small-bin limit one has
continuous distributions
(sometimes called ``extended''~\cite{barlow1990extended}),
which are standard and easily analysed.

>>>>

Worse, I disregarded the idea that every region should have a large
background expectation.
Normally, this is justified by the limitations of approximate statistical
methods, which work
``from as few as $\mathcal{O}(10)$ data events''~\cite{histfitter2014}.
But the Poisson likelihood works for infinitesimally small
expectations~\cite{skilling2009cosmology}, and in the small-bin limit one has
continuous distributions with Poisson normalizations
(sometimes called ``extended'' in high-energy
physics~\cite{barlow1990extended})
that are standard and easily analysed.
